On the probability of finding a nonphysical solution through shadowing\footnote{Preprint available at \cite{preprint}}

### 2020-11-18 main.tex
Updates from Overleaf

\author{Nisha Chandramoorthy and Qiqi Wang}

@@

\institute{           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           Center for Computational Science and Engineering, MIT, Cambridge, MA 02139, USA. Corresponding author email: \email{nishac@mit.edu}  \email{qiqi@mit.edu}. Preprint available at \cite{preprint}
}

@@

\begin{abstract}
Based on the shadowing property of dynamical systems, we expect that numerical solutions of governing equations lie close to a true solution -- a shadowing solution -- of the governing equation. This is used to justify, even when the governing equation is chaotic, that numerical solutions represent a true solution. However, shadowing solutions can be \emph{nonphysical}: they may not represent the long-term statistical behavior of an ensemble of true solutions. That is, the probability distribution of a shadowing solution can differ, often dramatically, from that of a solution starting from almost every initial condition. In this paper, we construct analytical examples of chaotic systems in which shadowing solutions are nonphysical. These examples also illustrate that the probability of finding a nonphysical shadowing solution can be 1. Through several analytical constructions, we note that the incorrect assumption of the physicality of shadowing raises questions on the trustworthiness of numerical solutions, and shadowing-based sensitivity analysis of chaotic systems.
\keywords{Numerical simulations \and Shadowing sensitivity analysis \and Chaotic systems}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\bibliographystyle{spmpsci}

>>>>

\author{Nisha Chandramoorthy \and Qiqi Wang}

@@

\institute{           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           Center for Computational Science and Engineering, MIT, Cambridge, MA 02139, USA. Corresponding author email: \email{nishac@mit.edu}  \email{qiqi@mit.edu}. }

@@

\begin{abstract}
In this work, we show that a small parameter perturbation can lead to a dramatic change in the statistics of a chaotic system. This theoretical observation implies that chaotic numerical simulations are not guaranteed to emulate the true  able to c ability of chaotic numerical simulations to capture the true long-term behavior of underlying governing equation. the failure of numerical simulations to capture the long-term statistical behavior of the governing equations. whether  the fidelity of chaotic numerical simulations to the underlying physics. 
Based on the shadowing property of dynamical systems, we expect that numerical solutions of governing equations lie close to a true solution -- a shadowing solution -- of the governing equation. This is used to justify, even when the governing equation is chaotic, that numerical solutions represent a true solution. However, shadowing solutions can be \emph{nonphysical}: they may not represent the long-term statistical behavior of an ensemble of true solutions. That is, the probability distribution of a shadowing solution can differ, often dramatically, from that of a solution starting from almost every initial condition. In this paper, we construct analytical examples of chaotic systems in which shadowing solutions are nonphysical. These examples also illustrate that the probability of finding a nonphysical shadowing solution can be 1. Through several analytical constructions, we note that the incorrect assumption of the physicality of shadowing raises questions on the trustworthiness of numerical solutions, and shadowing-based sensitivity analysis of chaotic systems.
\keywords{Numerical simulations \and Shadowing sensitivity analysis \and Chaotic systems}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\bibliographystyle{amm}
